MSOA Industrial Electricty and Gas maps

### 2021-08-09 MSOA non domestic Elec and Gas.Rmd
Changing elec variable name

```{r Mapping the electrcity consumption of the MSOAs Industrial Sector}
msoa_elecDatanondom$MSOA11CD <- msoa_elecDatanondom$ 'Middle Layer Super Output Area (MSOA) Code' 
msoa_merged_sf_nondom <-merge(msoa_sf_data, msoa_elecDatanondom)
ggplot2::ggplot(msoa_merged_sf_nondom) + 
  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
  scale_fill_continuous(name = "Electricity: Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Solent (all MSOAs)")
#mapping it
```
####Difference from 2010 to 2019
```{r Creating the mean electricty consumption from the industrial sector MOSA}
##BROKEN
NONDOMELEC_MSOA_2010<-readr::read_csv(paste0(dataFolder,"/energy/MSOA_NONDOM_2010.csv")
NONDOMELEC_MSOA_2019<-readr::read_csv(paste0(dataFolder,"/energy/MSOA_NONDOM_2019.csv")  
NONDOMELEC_MSOA_2010$nondomelec2010 <-NONDOMELEC_MSOA_2010$' Mean consumption (kWh per meter)'                                       
NONDOMELEC_MSOA_2019$nondomeelec2019<-NONDOMELEC_MSOA_2019$' Mean consumption (kWh per meter) '
merged_nondomelec <-merge(NONDOMELEC_MSOA_2010, NONDOMELEC_MSOA_2019, by = "Middle Layer Super Output Area (MSOA) Code", all=TRUE)
names(merged_nondomelec)
merged_nondomelec$nondomelec_diff<-merged_nondomelec$nondomeelec2019 - merged_nondomelec$nondomeelec2010
summary(merged_nondomelec)
```
```{r Mapping the difference in mean electricty consumption from the industrial sector MOSA}
merged_nondomelec$MSOA11CD <- merged_nondomelec$"Middle Layer Super Output Area (MSOA) Code"
msoa_nondom20102019 <- merge(msoa_sf_data, merged_nondomelec) #merging these
ggplot2::ggplot(msoa_nondom20102019) +
  geom_sf(aes(fill=nondom_diff))+ 
  scale_fill_continuous(name="Change in  mean electricty consumption for the industrial sector", low="green",high="red")+
  labs(caption ="Solent (all MSOAs)")
```
### Mapping Gas
####2019
```{r Loading in the MSOA gas consumption data for industry }
# gas consumption data for industry at MSOA level (pre downloaded)
inFile <-paste0(dataFolder, "energy/MSOA_NonDom_Gas_2019.csv")
msoa_gasDatanondom <- readr::read_csv(inFile)
head(msoa_gasDatanondom)
```

>>>>

```{r Mapping the electrcity consumption of the MSOAs Industrial Sector}
msoa_elecDatanondom$MSOA11CD <- msoa_elecDatanondom$ 'Middle Layer Super Output Area (MSOA) Code' 
msoa_merged_sf_nondom <-merge(msoa_sf_data, msoa_elecDatanondom)
ggplot2::ggplot(msoa_merged_sf_nondom) + 
  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
  scale_fill_continuous(name = "Electricity: Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Solent (all MSOAs)")
#mapping it
```
####Difference from 2010 to 2019
```{r Creating the mean electricty consumption from the industrial sector MOSA}
##BROKEN
ndelec_msoa_2010 <-readr::read_csv(paste0(dataFolder,"/energy/MSOA_NONDOM_2010.csv")
ndelec_msoa_2019 <-readr::read_csv(paste0(dataFolder,"/energy/MSOA_NONDOM_2019.csv")  
ndelec_msoa_2010$ndelec2010 <-ndelec_msoa_2010$' Mean consumption (kWh per meter)'                                       
ndelec_msoa_2019$ndelec2019 <-ndelec_msoa_2019$' Mean consumption (kWh per meter) '
merged_nondomelec <-merge(ndelec_msoa_2010, ndelec_msoa_2019, by = "Middle Layer Super Output Area (MSOA) Code", all=TRUE)
names(merged_ndelec)
merged_ndelec$ndelec_diff<-merged_ndelec$ndelec2019 - merged_ndelec$ndelec2010
summary(merged_ndelec)
```
```{r Mapping the difference in mean electricty consumption from the industrial sector MOSA}
merged_nondomelec$MSOA11CD <- merged_nondomelec$"Middle Layer Super Output Area (MSOA) Code"
msoa_nondom20102019 <- merge(msoa_sf_data, merged_nondomelec) #merging these
ggplot2::ggplot(msoa_nondom20102019) +
  geom_sf(aes(fill=nondom_diff))+ 
  scale_fill_continuous(name="Change in  mean electricty consumption for the industrial sector", low="green",high="red")+
  labs(caption ="Solent (all MSOAs)")
```
### Mapping Gas
####2019
```{r Loading in the MSOA gas consumption data for industry }
# gas consumption data for industry at MSOA level (pre downloaded)
inFile <-paste0(dataFolder, "energy/MSOA_NonDom_Gas_2019.csv")
msoa_gasDatanondom <- readr::read_csv(inFile)
head(msoa_gasDatanondom)
```
